### 2019-04-05 2-Chapters/5-Chapter/chapter5.tex
Galère ce chapitre 5, je sais pas trop quoi faire.
Started to write the « related works for other models » section in Chapter:5

@@

% ----------------------------------------------------------------------------
\section{Literature review of algorithms solving the ``no sensing'' case}
\label{sec:5:noSensingCase}

@@

>>>>

\paragraph{Abstract}

@@

% ----------------------------------------------------------------------------
\section{Many extensions of our models: literature review and numerical experiments}
\label{sec:5:literatureReviewOtherModels}

@@

\TODOL{Just a small sentence saying that we present here all the extensions of our models that we are aware of blabla}

\subsection{Unknown (fixed) number of players}
\label{sub:5:unknownNumberOfPlayers}

\TODOL{Present the model, quote the main papers, explain the difficulty and how XXX algorithm solves it!}

\subsection{Without sensing information}
\label{sub:5:withoutSensing}

\TODOL{Present the model, quote the main papers, explain the difficulty and how XXX algorithm solves it!}

\subsubsection{Additionnal numerical simulations}

\TODOL{Do some basic simulations and show !}

\subsection{With communication or coordination between players}
\label{sub:5:withCommunicationOrCoordination}

\TODOL{Present the model, quote the main papers, explain the difficulty and how XXX algorithm solves it!}

\subsection{Arrival and departures of players}
\label{sub:5:arrivalDepartures}

\TODOL{Present the model, quote the main papers, explain the difficulty and how XXX algorithm solves it!}

\subsection{With different arm utilities among players}
\label{sub:5:withDifferentMeansAmongPlayers}

\TODOL{Present the model, quote the main papers, explain the difficulty and how XXX algorithm solves it!}

\subsection{With malicious jammers}
\label{sub:5:withDifferentMeansAmongPlayers}

\TODOL{Present the model, quote the main papers, explain the difficulty and how XXX algorithm solves it!}

\subsection{Real-world demonstrations to validate some models}
\label{sub:5:USRPdemos}

Similarly to our demonstration of multi-armed bandit learning in an IoT network that we presented in the previous Chapter~\ref{chapter:4} in Section~\ref{sec:4:gnuradio},
we review in this section some related works, dating back from $2016$, who proposed a similar approach.
All the similar works that we are aware of also used USRP boards, and implemented the demonstration using either the Simulink and MATLAB softwares, or the GNU Radio software like we did \cite{Besson2018ICT}.

\TODOL{Present the model, quote the main papers, explain the difficulty and how XXX algorithm solves it!}

\subsection{Towards non-stationary multi-players MAB models}
\label{sub:5:towardsNonStationaryModels}

\TODOL{Present the model, quote the main papers, explain the difficulty and how XXX algorithm solves it!}
